---
title: Getting Organized - Part 1
author: ''
date: '2021-06-18'
slug: []
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2021-06-18T07:25:26-04:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
math: true
bibliography: ../../../static/bib/library.bib
type: book
graphic: true
jplayer: true
src_version: '425'
---
```{r setup, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
require(reticulate)
```

```{python, eval=TRUE, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
sys.path.append('../../../assets/python')

from ctns_make  import ctns_make  as CTNS_MAKE
from ctns_build import ctns_build as CTNS_BUILD
from ctns_flashcard_maker import flashcard_make as CTNS_FLASHCARD_MAKER
import ctns_form as CTNS

VERSION=425
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}

slide_list = [
    "rational_functionD8_2"
]

m_list = [ { 'name': s, 'qset':[s] , 'options':CTNS.FORM_SLIDE_1 } for s in slide_list ]

#q_list = [
#    {'name': 'quiz_abs_value_properties', 'options':CTNS.FORM_QUIZ_1 + ["count=14"], 'qset': slide_list}
#]
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
for m in m_list:
    CTNS_BUILD(target=m, process_support_files=False, version=VERSION, write_image=False, encrypt=False)
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
for m in q_list:
    CTNS_BUILD(target=m, process_support_files=True, version=VERSION, write_image=False, encrypt=False)
```

My goal here is to demonstrate how a student can create a study packet independently and in collaboration with others. 

[Boat load of practice, practice, and more practice]

Before I begin, however, I thought I would first google recommendations from others on the question, "how to study math." My first search results garnered the following quick summary [@Howto2019]:

1. Practice, practice, and more practice
2. Finish your homework.
3. Take extensive notes.
4. Ask for help
5. Believe in yourself.

### Practice what?

What new skill doesn't come from countless hours of practice? Music, sports, and academics, if not all trade skills, benefit from innumerable hours of practice. Nonetheless, my push back on No. 1 is, practice what?

:::{ .highlight .blue .reverse }
Effective practice begins with organization, and organization begins with patterns. Recognizing patterns in your math studies, and then categorizing these patterns into groups of problem types is key to effective study. 
:::

The advantage of organizing your study is that you may learn more about your math problems than simply the ability to solve a particular problem.

Your first order of business is to organize your work. That said, you must extract some sense of organization from your math studies. It is not enough to simply solve a particular problem, you need to rise above a problem, and look for commonality across similar problems.

When reading a textbook on Algebra 2, I found several ways to organize its content:

- **Countable sets** of equations or formulas
- **Inventory** of tools or steps
- **Patterns** of problems or questions
- **Flashcards** for vocabulary

Instead of being a student of math, suppose instead that you are a carpenter's apprentice rather than a student of math, and that your goal as a future carpenter is build a house. If you were an apprentice carpenter, you cannot act on such advice as, "Build many houses, then build many more." Such gross advice does not work. First, you need to know the countable sets of parts of a home: foundation, structure, siding, plumbing, electrical, rough carpentry, and roofing. Second, you need to know your tools: wood, hammer, nails, measures, drills, saws. And third, you need to know pattern layouts and details of typical rooms: kitchen, bedroom, bathroom, staircases, basements, and entry ways.

Before I speak to these types of organizations, let me offer a tangible metaphor to illustrate my point. Suppose you were an apprentice carpenter who wants to build houses, you cannot act on such advice as, "Build many houses, then build many more." Such gross advice does not work. First, you need to know the countable sets of parts of a home: foundation, structure, siding, plumbing, electrical, rough carpentry, and roofing. Second, you need to know your tools: wood, hammer, nails, measures, drills, saws. And third, you need to know pattern layouts and details of typical rooms: kitchen, bedroom, bathroom, staircases, basements, and entry ways.

The same goes for studying math. To say, "Practice, practice, and more practice" is like saying, "Build, build, and more build." Just as building houses requires organization from the start so too does studying and applying math.

Organizing the building of a house is quite tangible and visual. Organizing your studies in math is not quite so tangible. Therefore, we need to add abstraction to your organization beginning with countable sets, inventory of tools and steps, and patterns of problems or questions.

For example, you can organize problems aligned with a **countable set** of equations, such as the four equations for linear systems:

$$
\begin{gathered}
\textrm{ For } a,b,c, A, B, C, m \in \mathbb{R}
\end{gathered}
$$
$$
\begin{array}{r l}
\textrm{ Slope-intercept form} & y = mx+b, \textrm{ where } m \ne 0 \\
\textrm{ Point-slope form} & y - y_1 = m(x - x_1), \textrm{ where } m \ne 0 \\
\textrm{ General form} & Ax + By = C \\
\textrm{ Intercept-intercept form} & x/a + y/b = 1, \textrm{ where } a,b \ne 0
\end{array}
$$
Alternatively, you can organize topics around an **inventory** of tools, such as a set of properties and definitions for transforming a simple algebraic equation when solving for a variable:

$$
\textrm{ For } a,b,c \in \mathbb{R},
$$
$$
\begin{array}{r l}
\textrm{ Additive property of equality}       & \ \ a = b \ \equiv \ a+c = b+c \\
\textrm{ Multiplicative property of equality} & \ \ a = b \ \equiv \ a \cdot c = b \cdot c \\
\textrm{ Distributive property }              & \ \ a \cdot (b+c) = a \cdot b + a \cdot c \\
\textrm{ Definition of subtraction }          & \ \ a-b \ \equiv \ a + (-b)\\
\textrm{ Definition of division }             & \ \ a \div b \ \equiv \ a \cdot (1/b), \textrm{ where } b \ne 0 \\
\end{array}
$$

Different still, you can organize topics around **patterns** of problem types, such as different kinds of factoring problems for quadratic expressions:

$$
\begin{gathered}
\textrm{For } a, B, C, p, q,m,n \in \mathbb{R}
\end{gathered}
$$
$$
\begin{array}{r l}
\textrm{Binomial} & x^2 + ax = x (x+a) \\
\textrm{Difference of squares} & x^2 - a^2 = (x-a)(x+a) \\
\textrm{Guess-and-check} & x^2 +Bx + C = (x + p)(x + q), \\ & \textrm{where } p+q=B, \ p\, q=C \\
\textrm{Difference of squares Plus} & x^{2n} - a^{2m} = (x^n - a^m)(x^n + a^m), \\ & \textrm{where } m,n \gt 0
\end{array}
$$
And finally, you can also organize content by **how** you study. Flashcards have always been helpful for memorizing vocabulary words. The same is no less true for memorizing vocabulary in math. Memorizing the Axioms that define when a set is a Field is a clear example:

$$\textrm{For } a, b, c \in \mathbb{R}$$
$$
\begin{array}{r l}
\textrm{ Closure  }        & \ \ a+b \in \mathbb{R} \ \ \textrm{ and } \ \ a \cdot b \in \mathbb{R} \\
\textrm{ Identity }        & \ \ a + 0 = a \ \ \textrm{ and } \ \ a \cdot 1 = a \\
\textrm{ Inverse }         & \ \ a + (-a) = 0 \ \ \textrm{ and } \ \ a \cdot (1/a) = 1, \ a \ne 0\\
\textrm{ Commutative }     & \ \ a + b = b + a \ \ \textrm{ and } \ \ a \cdot b = b \cdot a \\
\textrm{ Associative }     & \ \ a + (b + c) = (a + b) + c \ \ \textrm{ and } \ \ a \cdot (b \cdot c )= (a \cdot b) \cdot c \\
\textrm{ Distributive }    & \ \ a \cdot (b + c) = a\cdot b + a \cdot c
\end{array}
$$

At least for the listed items in the first three organizations, countable sets, inventory, and patterns, you can further note for each particular item

- **when** an item applies to a problem,  
- **recognize** when to choose one item over another, and
- **collect** sample problems that highlight each.

----

can show an example
working with a type of problem
- Look for the visual patterns in your problem set, and then second,
- Re-group your problem set according to their pattern.

Here lies a great question for your teacher, "Please help me group the problems in my problem set according to their patterns."

Note, asking a question about how to group problems in a problem set is not the same as asking a question about what is going to be on the test.

### Organizing steps for factoring 

I am going to use the concept of factoring from Algebra I to demonstrate what I am talking about.

I am going to begin with a study pack outline specific to problem types,

- Title
- List of Names | Problem Types
- Example - Name | Problem Type - How to solve
- Mix of Examples - Name | Problem Type
- Flashcards Vocabulary | Names | Problem Types

Here is an alternative study pack outline specific to equations,

- Title
- List of Names | Equations 
- Example - Name | Equations - How to solve
- Mix of Examples - Name | Equations 
- Flashcards Vocabulary | Names | Equations 

### Factoring in Algebra I

In Algebra I, you see quite a few problem types when learning how to factor a binomial or trinomial. To begin with, you will likely be asked to factor a binomial:

Factor the following quadratic equation

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('rational_functionD8_4a')
```

From this example, you may recognize several key observations: 

- This expression is a **binomial** -- there are only two terms;
- This expression is a **quadratic** -- the term with the highest degree is a squared term, such as $x^2$ or $y^2$; and,
- Every term in this expression includes a variable, e.g., $x$ or $y$. There is no constant term.
- This expression motivates specific vocabulary: The Binomial, monomial, binomial, trinomial, greatest common factor, and quadratic

Let's call this problem type, "The Binomial: $x^2+ax$" and "The Binomial: $x^2-ax.$"   I find giving a name to a problem type helps me distinguish this problem type from others. 

I plan to name and count everything when comes to creating a study pack

For the two problem types, I record their name, shape, and steps to factor.

<div class="view">
<div class="view-title">
<strong>FACTORING</strong><br/>
Binomials
</div>
<div>
<div class="view-left">
<strong>Binomial</strong><br/><br/>
$\ \ 1) \ \ x^2 + ax$<br/><br/>
$\ \ 2) \ \ x^2 - ax$<br/><br/>
</div>
<div class="view-right">
Factor out the **greatest common factor**, e.g., $x.$
<br/><br/>$\ \ 1) \ \ x^2 + ax = x(x+a)$
<br/><br/>$\ \ 2)\ \ x^2 - ax = x(x-a)$
Descriptive notes:

- Binomial -- there are only two terms
- Quadratic -- term with highest degree is squared
- There is NO constant term -- all terms have an $x$
- Very simple to factor (Yay!)

</div>
</div>
</div>

<div class="view">
<div class="view-title">
<strong>FACTORING</strong><br/>
Binomials
</div>
<div>
<div class="view-left">
<strong>Find Binomials<div class="color-group color-mode-a"><div class="color-group-a">A</div></div></strong><br/><br/>
$\ \ 1) \ \ x^2 + ax$<br/><br/>
$\ \ 2) \ \ x^2 - ax$<br/><br/>
</div>
<div class="view-right">

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('rational_functionD8_4')
```
</div>
</div>
</div>

<div class="view">
<div class="view-title">
<strong>FACTORING</strong><br/>
Binomials
</div>
<div>
<div class="view-left">
<strong>Practice <div class="color-group color-mode-a"><div class="color-group-a">A</div></div></strong><br/><br/>
$\ \ 1) \ \ x^2 + ax$<br/><br/>
$\ \ 2) \ \ x^2 - ax$<br/><br/>
</div>
<div class="view-right">

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('rational_functionD8_4')
```
</div>
</div>
</div>

----

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('gen_factoring_the_binomial')
blogdown::shortcode('gen_poly_binomial')
blogdown::shortcode('gen_poly_monomial')
blogdown::shortcode('gen_poly_trinomial')
```

----



From this example alone, you can that one problem type

When I see this quadratic This problem is a question

Once you know the patterns, i.e., the categories of problems, then you can focus your effort on working specific categories, one category at a time. There is no benefit to work all kinds of problems pooled together unless you can see the patterns.



### Finish your homework is a marker

"Finish your homework" is a marker for academic success; it is not a marker for studying math. Generally speaking, if you cannot complete your lesson, you will likely be unsuccessful when it comes to your measured tests -- most instructors align homework with their course goals and, therefore, measured tests.

As a point of note, I tell all of my graduating seniors that they must finish every homework assignment when taking a class in college. The inability to complete a lesson is a tangible sign that a student must take evasive action quickly: double down on their studies, drop the class, or even change college majors. I remind my seniors that they do not want to score poorly on any college exam -- it is better to drop a course before an exam than to score poorly knowingly.

High school students do not have the same convenient option

"Take extensive notes" begs my first response: take extensive notes on what? Ask for help or, better yet, work with others is the first helpful recommendation from this shortlist. And finally, rounding the turn with "believe in yourself" sounds like the beginning of a phrase, when all else fails, believe in yourself.

To be fair, these five recommendations are not unreasonable if you were to ask someone else how they made it through college algebra. Digging deeper in the article that garnered my first search hit, I find a statement of shame.

> But maths really isn't impossible if you're willing to put in the work. Students often find the subject to be tedious or difficult because they haven't taken the time to understand the formulas and principles, mastered the basics, or practised enough.

The message here is that not learning math is the fault of the student: you did not learn the material because you were not willing to put in the work. It is on this point alone I find the problem with the mantra, practice, practice, practice.

> [Studying] Mathematics [requires] plenty of 'doing', and it's not a subject you can memorise from a textbook the night before an exam.

I agree with the point that one cannot study math in one night alone. LAs with learning almost any new activity, studying math takes planning and practice. 

few activities can bedemonstrating skill At some point in our math studies, we have all been given the assignment sheet of no less than 50 problems to complete for homework. You can easily imagine a sheet as shown below.

### References
