---
title: Combinatorics - Summary
author: ''
date: '2021-02-27'
slug: combinatorics-summary
categories: []
tags: []
subtitle: ''
summary: 'The following list of combinatoric identities is a running collection of those identities that I have used to date on my site. The summary is meant to be a quick reference list only without exposition.'
authors: []
lastmod: '2021-02-27T11:08:04-05:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---
The following list of combinatoric identities is a running collection of those identities that I have used to date on my site. The summary is meant to be a quick reference list only without exposition.

```{theorem, label="binomial-coefficient", name="The Binomial Coefficient"}
For non-negative $n$ and $0 \le k \le n$,

\begin{equation}
{n \choose k} = \frac {n!}{k!(n-k)!}
\end{equation}
  
is called a **binomial coefficient**.

```

```{theorem, label="binom-coef-one", name="Binomial Coefficient Identity"}
Let $n$ and $k$ be positive integers, where $k \le n$. Then

\begin{equation}
{n \choose k} = {n \choose n-k}
\end{equation}
```

```{r, echo=FALSE}
blogdown::shortcode_open("spoiler", text="Click to view: More information", .type="html")
```

**Proof**

\begin{aligned}
{n \choose k} = & \ \  \frac {n!}{k!(n-k)!} \\
              = & \ \  \frac {n!}{(n-k)!k!} \\
              = & \ \  \frac {n!}{(n-k)!(n-(n-k))!} \\[1em]
              = & \ \  {n \choose n-k} \\[1em]
                & & \rule{0.5em}{0.5em}
\end{aligned}

When noted in Pascal's Triangle, these two combinations are symmetric about the Triangle's center line for given values of $n$ and $k$ . For example, let $n=5$ and $k=1$, then we have
```{python, results='asis', echo=FALSE}
import pascal as ML
```

\begin{aligned}
{5 \choose 1} = & \ \ {5 \choose 5-1}  \\[1em]
              = & \ \ {5 \choose 4}    \\[1em]
              = & \ \ \bluebox{5}.
\end{aligned}

These two combinations are readily seen as symmetric about the center line in Pascal's Triangle

```{python, results='asis', echo=FALSE}
print(ML.pascals_triangle(6, combo="TRUE",
    highlight=[(5,1,'blue'), (5,4, 'blue')]))
```

and as numeric values

```{python, results='asis', echo=FALSE}
print(ML.pascals_triangle(6,
    highlight=[(5,1,'blue'), (5,4, 'blue')]))
```

```{r, echo=FALSE}
blogdown::shortcode_close("spoiler", .type="html")
```

```{theorem, label="the-binomial-theorem", name="The Binomial Theorem"}
The **binomial theorem** states for real or complex $a, b,$ and non-negative $n$,

\begin{equation}
(a+b)^n = \sum^n_{k=0} {n \choose k} a^{n-k}b^k
\end{equation}

where ${n \choose k} = \frac {n!}{k!(n-k)!}$ is a **binomial coefficient**.

```

```{r, echo=FALSE}
blogdown::shortcode_open("spoiler", text="Click to view: More information on 'The Binomial Theorem'", .type="html")
```

Related Posts

- [Pascal's Triangle](/post/pascal-s-triangle)
- [The Binomial Coefficient - Proof](/post/the-binomial-theorem-proof)

```{r, echo=FALSE}
blogdown::shortcode_close("spoiler", .type="html")
```

```{theorem, label="the-pascals-identity", name="Pascal's Identity"}
Let $n$ and $k$ be positive integers, where $k \le n$. Then

\begin{equation}
{ n \choose k} = {n-1 \choose k-1} + {n-1 \choose k}
\end{equation}
```


