---
title: 1.1 Number Sets
author: ''
date: '2021-06-07'
slug: 1-1-number-sets
categories: []
tags: []
subtitle: ''
summary: 'The number sets range from the set of integers $\mathbb{Z}$ to real numbers $\mathbb{R}$.'
authors: []
lastmod: '2021-06-07T10:00:37-04:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
math: true
type: book
graphic: true
jplayer: true
src_version: '402'
---
```{r setup, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
require(reticulate)
```

```{python, eval=TRUE, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
sys.path.append('../../../assets/python')

from ctns_make  import ctns_make  as CTNS_MAKE
from ctns_build import ctns_build as CTNS_BUILD
from ctns_flashcard_maker import flashcard_make as CTNS_FLASHCARD_MAKER
import ctns_form as CTNS

VERSION=402
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
flashcard_data = [

    {'set_name': 'func', 'name': 'gen_func_complex_numbers', 'filename': 'lib/gen_NT_CompS', 'orig_filename': 'lib/NT_CompS', 'front': 'Complex Numbers', 'frontstyle': '', 'back': '$$\\mathbb{C} = \\{a+bi\\,|\\,a,b \\in \\mathbb{R}, i^2=-1\\}$$<br/><br/> The set of <strong>complex numbers</strong> $$\\mathbb{C}$$ is the set of numbers $$a+bi$$ where $$a$$ and $$b$$ are real numbers and the imaginary number $$i$$ is the square root of negative one.', 'backstyle': 'font-size:95%', 'frontspeak': '', 'backspeak': 'The set of complex numbers is the set of numbers A plus B times I where A and B are real numbers and the imaginary number I is the square root of negative one.'}

  , {'set_name': 'func', 'name': 'gen_func_even_numbers', 'filename': 'lib/gen_NT_EvenS', 'orig_filename': 'lib/NT_EvenS', 'front': 'Even Numbers', 'frontstyle': '', 'back': '$$\\textrm{Even Numbers} = \\{n = 2k \\,|\\, k \\in \\mathbb{Z}\\}$$<br/><br/> The set of <strong>even numbers</strong> is the set of numbers $$2 k$$ where $$k$$ is an integer.', 'backstyle': '', 'frontspeak': '', 'backspeak': 'The set of Even Numbers is the set of numbers 2 times K where K is an integer.'}

  , {'set_name': 'func', 'name': 'gen_func_integer_numbers', 'filename': 'lib/gen_NT_IntS', 'orig_filename': 'lib/NT_IntS', 'front': 'Integer Numbers', 'frontstyle': '', 'back': '$$\\mathbb{Z} = \\{..., -2, -1, 0, 1, 2, ... \\}$$<br/><br/>The set of <strong>integer numbers</strong> $$\\mathbb{Z}$$ is the number zero, combined with the set of natural numbers and their opposites.', 'backstyle': '', 'frontspeak': '', 'backspeak': 'The set of integer numbers is the number zero, combined with the set of natural numbers and their opposites.'}

  , {'set_name': 'func', 'name': 'gen_func_irrational_numbers', 'filename': 'lib/gen_NT_IrrS', 'orig_filename': 'lib/NT_IrrS', 'front': 'Irrational Numbers', 'frontstyle': '', 'back': 'The set of <strong>irrational numbers</strong> is the set of all numbers that cannot be expressed as a quotient of one integer $$p$$ divided by another integer $$q$$, divided by zero excepted.', 'backstyle': '', 'frontspeak': '', 'backspeak': 'The set of irrational number is the set of all numbers that cannot be expressed as a quotient of one integer divided by another, divided by zero excepted.'}

  , {'set_name': 'func', 'name': 'gen_func_natural_numbers', 'filename': 'lib/gen_NT_NatS', 'orig_filename': 'lib/NT_NatS', 'front': 'Natural Numbers', 'frontstyle': '', 'back': '$$\\mathbb{N} = \\{1, 2, 3, ... \\}$$<br/><br/> The set of <strong>natural numbers</strong> $$\\mathbb{N}$$ is the set of counting numbers, 1, 2, 3, and so forth.', 'backstyle': '', 'frontspeak': '', 'backspeak': 'The set of natural numbers is the set of counting numbers, 1, 2, 3, and so forth.'}

  , {'set_name': 'func', 'name': 'gen_func_odd_numbers', 'filename': 'lib/gen_NT_OddS', 'orig_filename': 'lib/NT_OddS', 'front': 'Odd Numbers', 'frontstyle': '', 'back': '$$\\textrm{Odd Numbers} = \\{m = 2k+1 \\,|\\, k \\in \\mathbb{Z}\\}$$<br/><br/> The set of <strong>odd numbers</strong> is the set of numbers $$2k+1$$ where $$k$$ is an integer.', 'backstyle': 'font-size:90%;', 'frontspeak': '', 'backspeak': 'The set of Odd Numbers is the set of numbers 2 times K plus 1 where K is an integer.'}

  , {'set_name': 'func', 'name': 'gen_func_radicals', 'filename': 'lib/gen_NT_RadS', 'orig_filename': 'lib/NT_RadS', 'front': 'Radicals', 'frontstyle': '', 'back': 'The set of <strong>radicals</strong> is the set of all numbers that can be expressed as the roots of an integer.', 'backstyle': '', 'frontspeak': '', 'backspeak': ''}

  , {'set_name': 'func', 'name': 'gen_func_rational_numbers', 'filename': 'lib/gen_NT_RatS', 'orig_filename': 'lib/NT_RatS', 'front': 'Rational Numbers', 'frontstyle': '', 'back': '$$\\mathbb{Q} = \\{p/q | p,q \\in \\mathbb{z}, q \\neq 0 \\}$$<br/><br/> The set of <strong>rational numbers</strong> $$\\mathbb{Q}$$ is the set of numbers that can be expressed as a quotient of one integer $$p$$ divided by another integer $$q$$, divided by zero excepted.', 'backstyle': 'font-size:95%', 'frontspeak': '', 'backspeak': 'The set of rational numbers is the set of numbers that can be expressed as a quotient of one integer divided by another, divided by zero excepted.'}

  , {'set_name': 'func', 'name': 'gen_func_real_numbers', 'filename': 'lib/gen_NT_RealS', 'orig_filename': 'lib/NT_RealS', 'front': 'Real Numbers', 'frontstyle': '', 'back': 'The set of <strong>real numbers</strong> $$\\mathbb{R}$$ is the set of all numbers that can be expressed as a decimal number.', 'backstyle': '', 'frontspeak': '', 'backspeak': 'The set of real numbers is the set of all numbers that can be expressed as a decimal number.'}

  , {'set_name': 'func', 'name': 'gen_func_transcendental_numbers', 'filename': 'lib/gen_NT_TransS', 'orig_filename': 'lib/NT_TransS', 'front': 'Transcendental Numbers', 'frontstyle': '', 'back': 'The set of <strong>transcendental numbers</strong> is the set of numbers that cannot be expressed as the roots of an integer.', 'backstyle': '', 'frontspeak': '', 'backspeak': ''}

  , {'set_name': 'func', 'name': 'gen_func_whole_numbers', 'filename': 'lib/gen_NT_WholeS', 'orig_filename': 'lib/NT_WholeS', 'front': 'Whole Numbers', 'frontstyle': '', 'back': '$$\\mathbb{W} = \\{0, 1, 2, ... \\}$$<br/><br/>The set of <strong>whole numbers</strong> $$\\mathbb{W}$$ is the number zero, combined with the set of natural numbers.', 'backstyle': '', 'frontspeak': '', 'backspeak': 'The set of whole numbers is the number zero, combined with the set of natural numbers.'}

]

flashcard_list = CTNS_FLASHCARD_MAKER(flashcard_data);

print(flashcard_list)
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
#slide_list = [
#    'NT_NatS'
#  , 'NT_WholeS'
#  , 'NT_IntS'
#  , 'NT_RatS'
#  , 'NT_IrrS'
#  , 'NT_TransS'
#  , 'NT_RealS'
#  , 'NT_CompS'
#
#  , 'NT_EvenS'
#  , 'NT_OddS'
#  , 'NT_RadS'
#]

flashcard_list = ['gen_func_complex_numbers', 'gen_func_even_numbers', 'gen_func_integer_numbers', 'gen_func_irrational_numbers', 'gen_func_natural_numbers', 'gen_func_odd_numbers', 'gen_func_radicals', 'gen_func_rational_numbers', 'gen_func_real_numbers', 'gen_func_transcendental_numbers', 'gen_func_whole_numbers']

#flashcard_list = ['gen_func_complex_numbers', 'gen_func_even_numbers']

m_list = [ { 'name': s, 'qset':[s] , 'options':CTNS.FORM_FLASHCARD_1 } for s in flashcard_list ]

q_list = [
    {'name': 'quiz_number_sets', 'options':CTNS.FORM_QUIZ_1 + ["count=11"], 'qset': flashcard_list}
]
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
print([m['name'] for m in m_list])
for m in m_list:
    CTNS_BUILD(target=m, process_support_files=False, version=VERSION, write_image=True, encrypt=False)
    print("Built: %s" % m)
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
print([m['name'] for m in q_list])
for m in q_list:
    CTNS_BUILD(target=m, process_support_files=True, version=VERSION, write_image=False, encrypt=False)
```

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('quiz_number_sets')
```

The following number sets serve as the basis for operations in Algebra.

- Natural Numbers $\mathbb{N}$ (a.k.a., Counting Numbers)
- Whole Numbers $\mathbb{W}$
- Integers $\mathbb{Z}$
- Rational Numbers $\mathbb{Q}$
- Irrational Numbers
- Transcendental Numbers
- Real Numbers $\mathbb{R}$
- Complex Numbers $\mathbb{C}$

Separately, common groups of number sets are as follows.

- Even Numbers
- Odd Numbers
- Radicals

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('gen_func_complex_numbers')
blogdown::shortcode('gen_func_even_numbers')
blogdown::shortcode('gen_func_integer_numbers')
blogdown::shortcode('gen_func_irrational_numbers')
blogdown::shortcode('gen_func_natural_numbers')
blogdown::shortcode('gen_func_odd_numbers')
blogdown::shortcode('gen_func_radicals')
blogdown::shortcode('gen_func_rational_numbers')
blogdown::shortcode('gen_func_real_numbers')
blogdown::shortcode('gen_func_transcendental_numbers')
blogdown::shortcode('gen_func_whole_numbers')
```
