---
title: Binomial Coefficient Identities
author: ''
date: '2020-12-27'
slug: binomial-coefficient-identities
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2020-12-27T20:30:52-05:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
bibliography: [../../../static/bib/library.bib]
math: true
draft: true
---
This post summaries the Binomial Coefficient Identities that appear throughout data science and applied statistics. These identities are used regularly for manipulating expressions for deriving means and variations of certain distributions.
r 
$\renewcommand{\qedsymbolred}  {\color{red}{   \rule{0.5em}{0.5em}} }$
$\renewcommand{\qedsymbolblack}{\color{black}{ \rule{0.5em}{0.5em}} }$
$\renewcommand{\qedsymbolwhite}{\color{white}{ \rule{0.5em}{0.5em}} }$
$\renewcommand{\qedsymbol}                   { \rule{0.5em}{0.5em}}  $

----

### Number 1

\begin{equation}
{N \choose n} = \left( \frac Nn \right) {N-1 \choose n-1}.
(\#eq:one)
\end{equation}

```{r, echo=FALSE}
blogdown::shortcode_open("spoiler", text="<strong>Proof</strong>", .type="html")
```

When deriving the expected value of a random variable with a hypergeometric distribution, we use the identity Eq. \@ref(eq:one) above.

\begin{align}
{N \choose n} = \ & {N \choose n}         \\\\
              = \ & \frac{N!} {n! (N-n)!} \\\\
              = \ & \frac{N\cdot(N-1)!} {n\cdot(n-1)! (N-n)!} \\\\
              = \ & \left( \frac Nn \right) \frac{(N-1)!} {(n-1)! (N-n)!} \\\\
              = \ & \left( \frac Nn \right) {N-1 \choose n-1} \ \ \ \ \qedsymbol
\end{align}

For example [@Wackerly2002, pp. 65],

\begin{align}
\mathbb{E}[X] = \ & \sum_{x \in S} x \frac{{N_1 \choose x}{N_2 \choose {n-x}}}{\color{red} {N \choose n}} \\\\
              = \ & \sum_{x \in S} x \frac{N_1 !}{x! (N_1 - x)!} \frac{{N_2 \choose {n-x}}}{\color{red} \left(\frac Nn \right) {N-1 \choose n-1}}
\end{align}

```{r, echo=FALSE}
blogdown::shortcode_close("spoiler", .type="html")
```

### Number 2

\begin{equation}
{n \choose m} + {n \choose m+1 } = {n+1 \choose m+1}
(\#eq:two)
\end{equation}

```{r, echo=FALSE}
blogdown::shortcode_open("spoiler", text="<strong>Proof</strong>", .type="html")
```

\begin{align}
{n \choose m} + {n \choose m+1 } 
    = \ & \frac{n!}{m!(n-m)!} + \frac{n!}{(m+1)!(n-m-1)!} \\\\
    = \ & \frac{n!}{m!(n-m-1)!} \left[ \frac{1}{(n-m)} + \frac{1}{(m+1)} \right]\\\\
    = \ & \frac{n!}{m!(n-m-1)!} \left[ \frac{(m+1) + (n-m)}{(m+1)(n-m)} \right]\\\\
    = \ & \frac{n!}{m!(n-m-1)!} \left[ \frac{n+1}{(m+1)(n-m)} \right]\\\\
    = \ & \frac{(n+1)!}{m!(n-m-1)!} \left[ \frac{1}{(m+1)(n-m)} \right]\\\\
    = \ & \frac{(n+1)!}{(m+1)!(n-m-1)!} \left[ \frac{1}{(n-m)} \right]\\\\
    = \ & \frac{(n+1)!}{(m+1)!(n-m)!} \\\\
    = \ & \frac{(n+1)!}{(m+1)!((n+1)-(m+1))!} \\\\
    = \ & {n+1 \choose m+1 } \ \ \ \ \qedsymbol
\end{align}

```{r, echo=FALSE}
blogdown::shortcode_close("spoiler", .type="html")
```

### Reference
