---
title: MG 2.4
author: ''
date: '2021-07-02'
slug: mg-2-4
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2021-07-02T15:51:16-04:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
type: book
graphic: true
math: true
jplayer: true
src_version: '410'
---

Linear inequality is the same as a linear equation, except

- Linear inequality uses $\lt, \gt, \le, \ge$
- Linear equation uses $=$.

:::{.highlight .blue .reverse }
## Linear Inequality in One Variable

A linear inequality in one variable is an inequality that can be written in the form 
$$ax+b \lt c$$
where $a$, $b$, and $c$ are real numbers and $a \ne 0$.
:::

:::{.highlight .blue .reverse }
## Linear Equation in One Variable

A linear equation in one variable is an equatino that can be written in the form 
$$ax+b = c$$
where $a$, $b$, and $c$ are real numbers and $a \ne 0$.
:::
----

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('gen_linear_inequality_in_one_variable')
blogdown::shortcode('gen_solution_of_an_inequality')
blogdown::shortcode('gen_solution_set_of_an_inequality')
```

----

```{r setup, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
require(reticulate)
```

```{python, eval=TRUE, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
sys.path.append('../../../assets/python')

from ctns_make  import ctns_make  as CTNS_MAKE
from ctns_build import ctns_build as CTNS_BUILD
from ctns_flashcard_maker import flashcard_make as CTNS_FLASHCARD_MAKER
import ctns_form as CTNS

VERSION=410
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
flashcard_data = [

    { 
    
      #################################################################################
      
      'name': 'gen_linear_inequality_in_one_variable', 
      
      'front': 'Linear inequality in one variable', 
      'back': 'The linear inequality in one variable is an inequality that can be written in the form $|ax+b \lt c|$ where $$a$$, $$b$$, and $$c$$ are real numbers and $$a \\ne 0$$.', 

      'backspeak': 'The linear in equality in one variable is an inequality that can be written in the form -- eh times exx plus c is less than see -- where eh, bee, and see are real numbers and eh is not equal to zero.'
    
    }, { 
    
      #################################################################################
      
      'name': 'gen_solution_of_an_inequality', 
      
      'front': 'A solution of an inequality', 
      'back': 'A solution of an inequality<br/>is a value of the variable that makes the inequality a true statement.', 

    }, { 
    
      #################################################################################
      
      'name': 'gen_solution_set_of_an_inequality', 
      
      'front': 'The solution set of an inequality', 
      'back': 'The solution set of an inequality<br/> is the set of all solutions.', 

    }

]

#flashcard_list = CTNS_FLASHCARD_MAKER(flashcard_data);

#print(flashcard_list)
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
flashcard_list = CTNS_FLASHCARD_MAKER(flashcard_data);

flashcard_list = ['gen_solution_of_an_inequality']

#flashcard_list = ['gen_func_complex_numbers', 'gen_func_even_numbers']

m_list = [
  { 'name': s, 'qset':[s] , 'options':CTNS.FORM_FLASHCARD_1 } for s in flashcard_list 
]

q_list = [
  {'name': 'quiz_mg_2_4', 'options':CTNS.FORM_QUIZ_1 + ["count=%s" % len(flashcard_list)], 'qset': flashcard_list}
]
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
#print([m['name'] for m in m_list])
for m in m_list:
    CTNS_BUILD(target=m, process_support_files=True, version=VERSION, write_image=False, encrypt=False)
    #print("Built: %s" % m)
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
#print([m['name'] for m in q_list])
for m in q_list:
    CTNS_BUILD(target=m, process_support_files=False, version=VERSION, write_image=False, encrypt=False)
```

```{r eval=FALSE, echo=FALSE}
blogdown::shortcode('quiz_mg_2_4')
```

----

```{r eval=FALSE, echo=FALSE}
blogdown::shortcode('gen_linear_inequality_in_one_variable')
blogdown::shortcode('gen_solution_of_an_inequality')
blogdown::shortcode('gen_solution_set_of_an_inequality')
```
