---
title: Notes on R for Data Science
author: ''
date: '2021-01-04'
slug: notes-on-r-for-data-science
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2021-01-04T16:39:58-05:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
math: true
bibliography: ["../../../static/bib/library.bib"]
---

This post is my detailed walk-through of the text, __R For Data Science__ [@Wickham2016a]. My plan is to have a set of pages each related to a chapter or section in the book. This text is also available online [@Wickham2016b].

### The Online Book

[R for Data Science](https://r4ds.had.co.nz/r-markdown.html)

### Chapter 1. Data Visualization with ggplot2

Loading the library.

```{r, include=FALSE,message=FALSE,warning=FALSE}
library(tidyverse)
```

Displaying the data frame for 'mpg'.

```{r}
mpg
```

Showing help on mpg by using ?mpg. Help information prints to the console for R Markdown.

```{r}
?mpg
```

Here is my first plot using ggplot. This plot puts **displ** on the $x$-axis, and **hwy** on the $y$-axis, where 'displ' denotes engine displacement in liters and 'hwy' denotes hwy miles per gallon.

At a minimum, I can see that there is a negative relationship (correlation) between hwy and displ: the greater the displacement, the lower the miles-per-gallon. This makes sense: a gass guzzler (an 8 cylinder car) is going to have bad gas mileage.

```{r cars, fig.cap = "Write your Figure caption here."}
plot(cars)
```

```{r, fig.cap="A plot of MPG with DISPL(y) vs HWY(x)"}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy))
```
As an alternative, I may also invoked ggplot using the following syntax:

```r
p <- ggplot(mtcars, aes(wt, mpg))
p + geom_point()
```

The first argument to ggplot() sets the data set to use, e.g., 'mpg',

    ggplot(data = mpg).
    
The expression PLUS geom_point() adds a graphic layer to this plot in the form of a scatter plot.

    geom_point(mapping = aes(x = displ, y = hwy))
    
The argument $x=$ and $y=$ reference the $x$-axis and $y$-axis, respectively.

### Building up a scatter plot layer by layer.

I begin with the basic data for $x$-axis and $y$-axis, respectively.

```{r}
p <- ggplot(mtcars, aes(wt, mpg))
```

Then, I can build the first B&W plot for the data.

```{r}
p + geom_point()
```
Next, I can a third variable using **color**.

```{r}
p + geom_point(aes(colour = factor(cyl)))
```

Or, I can that third variable using **shape**.

```{r}
p + geom_point(aes(shape = factor(cyl)))
```

Even still, I can that third variable using **size**.

```{r}
p + geom_point(aes(size = factor(qsec)))
```

### Another alternative is to use ALPHA when you have a lot of data

```{r}
d <- ggplot(diamonds, aes(carat, price))
d + geom_point(alpha = 1/10)
```

```{r}
d <- ggplot(diamonds, aes(carat, price))
d + geom_point(alpha = 1/20)
```

```{r}
d <- ggplot(diamonds, aes(carat, price))
d + geom_point(alpha = 1/100)
```

### And still another approach is to color line and fill differently

```{r}
ggplot(mtcars, aes(wt, mpg)) +
  geom_point(shape = 21, colour = "black", fill = "white", size = 5, stroke = 5)
```

### References
