---
title: Delete this too
author: ''
date: '2021-03-14'
slug: delete-this-too
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2021-03-14T10:23:42-04:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
draft: true
---

- https://stackoverflow.com/questions/58219503/difference-between-read-htmlurl-and-read-htmlcontentgeturl-text
- https://www.datacamp.com/community/tutorials/r-web-scraping-rvest
- https://stat4701.github.io/edav/2015/04/02/rvest_tutorial/
- https://stackoverflow.com/questions/48373138/scraping-the-content-of-all-div-tags-with-a-specific-class
- https://www.analyticsvidhya.com/blog/2017/03/beginners-guide-on-web-scraping-in-r-using-rvest-with-hands-on-knowledge/

````{=html}
```{r, eval=FALSE, echo=FALSE, results='asis'}
library(httr)
r <- GET("https://testcite.com/showcase3/?target=rational-functionD5-5")
cat(content(r, "text"))
```
````

````{=html}
```{r, eval=FALSE, echo=FALSE}
library(httr)
library(rvest)
library(XML)

r <- read_html("https://testcite.com/showcase/?target=rational-functionD5-5")

metas <- r %>% 
  html_nodes("body *")

cat(toString.XMLNode(metas))
```
````

```{r, eval=FALSE, echo=FALSE}
library(httr)
library(rvest)
library(XML)

#r <- read_xml("https://testcite.com/showcase/?target=rational-functionD5-5")
#r <- read_html("https://testcite.com/showcase/?target=rational-functionD5-5")
#r <- GET("https://testcite.com/showcase/?target=rational-functionD5-5")
con <- curl("https://testcite.com/showcase3/?target=rational-functionD5-5")
open(con)

# Get 3 lines
out <- readLines(con, warn=FALSE)
cat(out)#, sep = "\n")

#toString.XMLNode(r)

#bodyInner <- r %>% html_node("body") %>% html_nodes("*")

#out <- readLines(r, warn=TRUE)
      #out <- readLines(head, warn=FALSE)
      #cat(out)#, sep = "\n")

#cat(out)

#cat(toString.XMLNode(bodyInner))
#cat(bodyInner)

#print(html_nodes(content(r), "head meta"))
#print(html_nodes(content(r), "head style"))
#print(html_nodes(content(r), "head link[rel='dns-prefetch']"))
#print(html_nodes(content(r), "head link[rel='alternate']"))
##stylesheet_href     = html_nodes(content(r), "head link[rel='stylesheet']") %>% html_attr("href")
#stylesheet_href    = html_nodes(content(r), "head link[rel='stylesheet']") %>% html_name()
##stylesheet_text     = html_nodes(content(r), "head link[rel='stylesheet']") %>% html_text() #toString.XMLNode()
##stylesheet_children = html_nodes(content(r), "head link[rel='stylesheet']") %>% html_children() #%>% toString.XMLNode()
##javascript_src      = html_nodes(content(r), "head script[type='text/javascript']") %>% html_attr("src")
##javascript_children = html_nodes(content(r), "head script[type='text/javascript']") %>% html_children() #%>% toString.XMLNode()
##body                = html_nodes(content(r), "*") #%>% html_children()

#print("************** Javascript src")
#print(javascript_src)
#print(javascript_children[1])
#print("************** Stylesheet href")
#print(stylesheet_href)
#print(stylesheet_children)
#print("************** Stylesheet innerHtml")
#print(stylesheet_text)
##print(body)

```

````{=html}
```{r, eval=FALSE, echo=FALSE}
library(httr)
library(rvest)
library(XML)

r <- read_html("https://testcite.com/showcase/?target=rational-functionD5-5")
#r <- GET("https://testcite.com/showcase/?target=rational-functionD5-5")

#toString.XMLNode(r)

metas <- r %>% 
  html_nodes("body *")

cat(toString.XMLNode(metas))

#print(html_nodes(content(r), "head meta"))
#print(html_nodes(content(r), "head style"))
#print(html_nodes(content(r), "head link[rel='dns-prefetch']"))
#print(html_nodes(content(r), "head link[rel='alternate']"))
##stylesheet_href     = html_nodes(content(r), "head link[rel='stylesheet']") %>% html_attr("href")
#stylesheet_href    = html_nodes(content(r), "head link[rel='stylesheet']") %>% html_name()
##stylesheet_text     = html_nodes(content(r), "head link[rel='stylesheet']") %>% html_text() #toString.XMLNode()
##stylesheet_children = html_nodes(content(r), "head link[rel='stylesheet']") %>% html_children() #%>% toString.XMLNode()
##javascript_src      = html_nodes(content(r), "head script[type='text/javascript']") %>% html_attr("src")
##javascript_children = html_nodes(content(r), "head script[type='text/javascript']") %>% html_children() #%>% toString.XMLNode()
##body                = html_nodes(content(r), "*") #%>% html_children()

#print("************** Javascript src")
#print(javascript_src)
#print(javascript_children[1])
#print("************** Stylesheet href")
#print(stylesheet_href)
#print(stylesheet_children)
#print("************** Stylesheet innerHtml")
#print(stylesheet_text)
##print(body)

```
````

```{r, eval=TRUE, echo=FALSE}
library(httr)
library(rvest)

r  <- read_html("https://testcite.com/showcase/?target=rational-functionD5-5")
r3 <- read_html("https://testcite.com/showcase3/?target=rational-functionD5-5")
#r <- GET("https://testcite.com/showcase/?target=rational-functionD5-5")

#print(r)

#html_nodes(content(r), "div")

print("************* HEAD *************")

head_metas   <- r %>% html_nodes(" head meta")
head_links   <- r %>% html_nodes(" head link")
head_scripts <- r %>% html_nodes(" head script")
head_styles  <- r %>% html_nodes(" head style")

#print(head_metas)
#print(head_links)
#print(head_scripts)
#print(head_styles)

print("************* BODY *************")

body         <- r %>% html_nodes(" body")
body_div     <- r %>% html_nodes(" body div")
body_span    <- r %>% html_nodes(" body span")
body_links   <- r %>% html_nodes(" body link")
body_scripts <- r %>% html_nodes(" body script")
body_styles  <- r %>% html_nodes(" body style")

body3        <- r3 %>% html_nodes(" body")

cat(paste(body, collapse='' ))
#print(body_metas)
#print(body_links)
#print(body_scripts)
#print(body_styles)

print("************* BODY3 *************")

cat(paste(body3, collapse='' ))
#rating
#print(html_nodes(content(r), "head"))
#print(r)
#for (head in html_nodes(content(r), "head")) {
#      print(head)
      #out <- readLines(head, warn=FALSE)
      #cat(out)#, sep = "\n")
#}
#out <- readLines(con, warn=FALSE)
#cat(out)#, sep = "\n")
```

```{r, eval=FALSE, echo=FALSE}
library(httr)
library(rvest)

r <- GET("https://testcite.com/showcase/?target=rational-functionD5-5")
#print(html_nodes(content(r), "head"))
for (head in html_nodes(content(r), "head")) {
      print(head)
      #out <- readLines(head, warn=FALSE)
      #cat(out)#, sep = "\n")
}
#out <- readLines(con, warn=FALSE)
#cat(out)#, sep = "\n")
```

````{=html}
```{r, eval=FALSE, echo=FALSE, results='asis'}
library(httr)
library(rvest)
r <- GET("https://testcite.com/showcase3/?target=rational-functionD5-5")
#cat(content(r, "text"))
#print(html_nodes(content(r), "div"))
for (div in html_nodes(content(r), "div")) {
      cat(div)
}
```
````

```{r, eval=FALSE, echo=FALSE, results='asis'}
library(httr)
library(crayon)
r <- GET("https://testcite.com/showcase3/?target=rational-functionD5-5")
cat(strip_style(content(r, "text")))
```

