---
title: New Rotation On Solids
author: ''
date: '2020-12-24'
slug: new-rotation-on-solids
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2020-12-24T12:14:41-05:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
draft: true
graphic: false
graphic_3d: true
asset: [ ]
google: false
---

On this page is a demonstration on how to invoke the routines for rotation of solids. My plan is to put each of the assorted types of rotations on this page. And, I plan to clean up the expressions so that they are invoked in a proper style for R Studio and Hugo.


<div id='ctns-3d-graph'></div>
<div id='MY_GRAPH'></div>
<div id='WebGL-output-X'></div>
<div id='Stats-output-X'></div>  

````{=html}
```{r, eval=FALSE, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
library(httr)
library(rvest)
library(xml2)

r3 <- read_html("https://testcite.com/showcase3/?target=rational-functionD5-5")

body3        <- r3 %>% html_nodes(" body *")

cat(paste(body3, collapse='' ))
```
````


````{=html}
```{r, eval=FALSE, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
library(httr)
library(rvest)
library(xml2)

#r3 <- read_html("https://testcite.com/showcase3/?target=test-linearQ15-9c")
#r3 <- read_html("https://testcite.com/showcase3/?target=test-linearQ15-9c,linearQ15-9d,linearQ15-12b")
r3 <- read_html("https://testcite.com/showcase3/?style=rwu&target=complexQ1,imagineQ1,imagineQ2")

ctns_body           <- r3 %>% html_nodes(" body div.ctns-body")
ctns_quiz_container <- r3 %>% html_nodes(" body div.ctns-quiz-container")
ctns_button_group   <- r3 %>% html_nodes(" body div.ctns-button-group")
ctns_results        <- r3 %>% html_nodes(" body div.ctns-results")
ctns_script         <- r3 %>% html_nodes(" body script")

cat(paste(ctns_body,           collapse='' ))
cat(paste(ctns_quiz_container, collapse='' ))
cat(paste(ctns_script,         collapse='' ))
cat(paste(ctns_button_group,   collapse='' ))
cat(paste(ctns_results,        collapse='' ))
```
````

```{js, eval=TRUE, echo=FALSE}
document.addEventListener("THREE", function(event) {

    var TML_MATH3D = window.TML_MATH3D || {};
    var handleQ = $('#MY_GRAPH');

    // My-Graph-3
    //
    TML_MATH3D.init({})
        .createCylinderSet({
            style:"rectangle",
            plane:"xy-plane",
            rotation:"primary",
            color:"red",
            addToScene:true,
            addToRotation:true,
            pickOne:false})
        .render();

  });
```
