---
title: 1.1 Number Sets
author: ''
date: '2021-06-07'
slug: 1-1-number-sets
categories: []
tags: []
subtitle: ''
summary: 'The number sets range from the set of integers $\mathbb{Z}$ to real numbers $\mathbb{R}$.'
authors: []
lastmod: '2021-06-07T10:00:37-04:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
math: true
type: book
graphic: true
jplayer: true
src_version: '253'
---
```{r setup, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
require(reticulate)
```

```{python, eval=TRUE, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
sys.path.append('../../../assets/python')

from ctns_make  import ctns_make  as CTNS_MAKE
from ctns_build import ctns_build as CTNS_BUILD
import ctns_form as CTNS

VERSION=253
```

```{python, eval=TRUE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
slide_list = [
    'NT_NatS'
  , 'NT_WholeS'
  , 'NT_IntS'
  , 'NT_RatS'
  , 'NT_IrrS'
  , 'NT_TransS'
  , 'NT_RealS'
  , 'NT_CompS'

  , 'NT_EvenS'
  , 'NT_OddS'
  , 'NT_RadS'
]

m_list = [ { 'name': s, 'qset':[s] , 'options':CTNS.FORM_FLASHCARD_1 } for s in slide_list ]

q_list = [
    {'name': 'quiz_number_sets', 'options':CTNS.FORM_QUIZ_1 + ["count=11"], 'qset': slide_list}
]
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
for m in m_list:
    CTNS_BUILD(target=m, process_support_files=False, version=VERSION, write_image=True, encrypt=False)
```

```{python, eval=TRUE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
for m in q_list:
    CTNS_BUILD(target=m, process_support_files=True, version=VERSION, write_image=False, encrypt=False)
```

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('quiz_number_sets')
```

The following number sets serve as the basis for operations in Algebra.

- Natural Numbers $\mathbb{N}$ (a.k.a., Counting Numbers)
- Whole Numbers $\mathbb{W}$
- Integers $\mathbb{Z}$
- Rational Numbers $\mathbb{Q}$
- Irrational Numbers
- Transcendental Numbers
- Real Numbers $\mathbb{R}$
- Complex Numbers $\mathbb{C}$

Separately, common groups of number sets are as follows.

- Even Numbers
- Odd Numbers
- Radicals

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('NT_NatS')
blogdown::shortcode('NT_WholeS')
blogdown::shortcode('NT_IntS')
blogdown::shortcode('NT_RatS')
blogdown::shortcode('NT_IrrS')
blogdown::shortcode('NT_TransS')
blogdown::shortcode('NT_RealS')
blogdown::shortcode('NT_CompS')

blogdown::shortcode('NT_EvenS')
blogdown::shortcode('NT_OddS')
blogdown::shortcode('NT_RadS')
```
