---
title: When is a function linear
author: ''
date: '2021-03-18'
slug: when-is-a-function-linear
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2021-03-18T14:30:45-04:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
graphic: true
math: true
---
```{r setup, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
require(reticulate)
```

```{python, eval=TRUE, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
sys.path.append('../../../assets/python')

from ctns_make import ctns_make as CTNS_MAKE
from ctns      import ctns as CTNS
```

A function is <strong>linear</strong> if its graph forms a straight-line. 

```{python, eval=TRUE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
CTNS(match='linearQ15-9c', opt_ctns = [
  "no_controls",
  "no_buttons",
  "quiz_css='margin: 2em 1em 2em 1em;'", 
])
```

```{r, echo=FALSE}
blogdown::shortcode_open("spoiler", text="<strong>Notes</strong>", .type="html")
```

See a straight-line graph? Think linear function, as in <strong>LINE</strong>ar function. A linear function is called <em>linear</em> precisely because its graph is a straight line. 

The reverse situation is true, too. If the graph of a function is a straight-line, then that function is a <em>linear</em> function. Linear functions and straight-line graphs go hand-in-hand.

```{r, echo=FALSE}
blogdown::shortcode_close("spoiler", .type="html")
```

