---
title: 1.3. Function Types
author: ''
date: '2021-05-08'
slug: 1-3-function-types
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2021-05-08T07:46:46-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
math: true
type: book
graphic: true
jplayer: true
---
```{r setup, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
require(reticulate)
```

```{python, eval=TRUE, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
sys.path.append('../../../assets/python')

from ctns_make  import ctns_make  as CTNS_MAKE
from ctns_build import ctns_build as CTNS_BUILD
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
# Start with creating each flashcard individually.
m_list = [
    ['func_absolute_valueS']
]

for m in m_list:
    CTNS_MAKE(target=m)
    CTNS_BUILD(target=m, id=m[0], image_target=m[0], opt_ctns = [ 
        "flashcard"
      , "no_controls"
      , "quiz_container_css='width:100%;'"
       ])
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
# Start with creating each flashcard individually.
m_list = [
    'axis_x_axis'
#    'func_absolute_value'
]

for m in m_list:
    CTNS_MAKE(match=m)
    CTNS_BUILD(match=m, id=m, image_target=m, opt_ctns = [ 
        "slide"
      , "no_divide"
      , "no_controls"
      , "no_buttons"
      , "css='padding:0'"
      , "quiz_container_css='padding:0;'"
    ])
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
# Start with creating each flashcard individually.
# Working https://www.intmath.com/cg3/jsxgraph-axes-ticks-grids.php
m_list = [
    ['abs_value_1']
  # ['abs_value_2']
]

for m in m_list:
    CTNS_MAKE(target=m)
    CTNS_BUILD(target=m, id=m[0], version=15, image_target=m[0], opt_ctns = [ 
        "slide"
      , "no_divide"
      , "no_buttons"
      , "css='padding:0'"
      , "quiz_container_css='padding:0;'"
      , "dynamic"
    ])
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
# Start with creating each flashcard individually.
# Working https://www.intmath.com/cg3/jsxgraph-axes-ticks-grids.php
m_list = [
    ['abs_value_3']
  , ['abs_value_4']
]

for m in m_list:
    CTNS_MAKE(target=m)
    CTNS_BUILD(target=m, id=m[0], image_target=m[0], opt_ctns = [ 
        "slide"
      , "no_divide"
      , "no_controls"
      , "no_buttons"
      , "css='padding:0'"
      , "quiz_container_css='padding:0;'"
    ])
```

## Absolute Value

The definition of the Absolute Value states,

\begin{equation}
|x| =  
\begin{cases}
\ \ \ x, & \text{if } \ x \ge 0 \\
-x, & \text{if } \ x \lt 0
\end{cases}
\end{equation}

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('func_absolute_valueS')
```

## Examples

For example, 

\begin{equation}
|3| = 3.
\end{equation}

The number $3$ is positive, in which case the equality
$|3| = 3$ follows from the
definition of absolute value for positive numbers,

\begin{equation}
|x| = x \ \ \ \text{when } x \ge 0.
\end{equation}

On the other hand,

\begin{aligned}
|-5| = \ & --5 \\
     = \ & 5.
\end{aligned}

The number $-5$ is negative, in which case 
the equality $|-5| = 5$ follows from
the definition of absolute for negative numbers,

\begin{equation}
|x| = --x \ \ \ \text{when } x \lt 0.
\end{equation}

Try some examples for yourself.

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_1')
```

## Distance to Zero

The Absolute Value of a number can also be thought of as that number's distance to zero
when graphing the number on a number line.

Consider the absolute value of $3$, where

\begin{equation}
|3| = 3.
\end{equation}

When graphed on a number line, it is clear that the number $3$ is three units from zero.

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_3')
```

Similarly, consider the absolute value of $-5$, where

\begin{equation}
|-5| = 5.
\end{equation}

When graphed on a number line, it is clear that the number $-5$ is five units from zero.

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_4')
```

Try some distance examples for yourself.

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_2')
```

## Property 1: $|x| \ = \ c$

When the absolute value of a
variable $x$ equals a number $c$, as in

\begin{equation}
|x| = c,
\end{equation}

then by the definition of the absolute value,

\begin{equation}
x = \ \pm \ c,
\end{equation}

which says that the variable $x$ equals either positive $c$ or negative $c$. 

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
# Start with creating each flashcard individually.
m_list = [
    ['abs_value_prop_1S']
]

for m in m_list:
    CTNS_MAKE(target=m)
    CTNS_BUILD(target=m, id=m[0], preview=True, image_target=m[0], opt_ctns = [ 
        "flashcard"
      , "no_controls"
      , "quiz_container_css='width:100%;'"
       ])
```

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_prop_1S')
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
# Start with creating each flashcard individually.
# Working https://www.intmath.com/cg3/jsxgraph-axes-ticks-grids.php
m_list = [
    ['abs_value_prop_1']
]

for m in m_list:
    CTNS_MAKE(target=m)
    CTNS_BUILD(target=m, id=m[0], version=16, image_target=m[0], opt_ctns = [ 
        "slide"
      , "no_divide"
      , "no_buttons"
      , "css='padding:0'"
      , "quiz_container_css='padding:0;'"
      , "dynamic"
    ])
```

Try these examples for yourself.

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_prop_1')
```

When graphing $|x| = c$ on the number line, you are going to label two points on the line, one point on the line for plus $c$ and another point for minus $c.$

Try for yourself.

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
# Start with creating each flashcard individually.
# Working https://www.intmath.com/cg3/jsxgraph-axes-ticks-grids.php
m_list = [
    ['abs_value_prop_line_1']
]

for m in m_list:
    CTNS_MAKE(target=m)
    CTNS_BUILD(target=m, id=m[0], version=20, image_target=m[0], opt_ctns = [ 
        "slide"
      , "no_divide"
      , "no_buttons"
      , "css='padding:0'"
      , "quiz_container_css='padding:0;'"
      , "dynamic"
    ])
```

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_prop_line_1')
```

## Using Property 1

When you see an absolute value expression involving a variable $x$ and constant $c$, you can solve for the variable using Property 1.

For example, consider the expression

\begin{equation}
|x - 3| = 5.
\end{equation}

Applying Property 1 to this expression gives you a new expression,

\begin{equation}
x - 3 = \pm 5.
\end{equation}

You can re-write this new expression into two separate expressions, 

\begin{align}
x - 3 & = \ + 5, and \\\\
x - 3 & = \ - 5.
\end{align}

Solve for $x$ for each case:

\begin{align}
    x - 3 & = \ 5 \\
x - 3 + 3 & = \ 5 + 3\\
    x & = \ 8,
\end{align}

and

\begin{align}
    x - 3 & = \ - 5 \\
x - 3 + 3 & = \ - 5 + 3 \\
        x & = \ - 2.
\end{align}

```{python, eval=TRUE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
# Start with creating each flashcard individually.
# Working https://www.intmath.com/cg3/jsxgraph-axes-ticks-grids.php
m_list = [
     ['abs_value_prop_line_2']
]

for m in m_list:
    CTNS_MAKE(target=m)
    CTNS_BUILD(target=m, id=m[0], version=20, image_target=m[0], opt_ctns = [ 
        "slide"
      , "no_divide"
      , "no_buttons"
      , "no_controls"
      , "css='padding:0'"
      , "quiz_container_css='padding:0;'"
    ])
```

Graphing these two values of $x$ on the number line gives you

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_prop_line_2')
```


----

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('axis_x_axis')
#blogdown::shortcode('func_absolute_value')
```

