---
title: CitePrep Math Examples
author: ''
date: '2021-03-17'
slug: citeprep-math-examples
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2021-03-17T16:27:38-04:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
graphic: true
math: true
---
On this page is a demonstration on how to invoke the routines for rotation of solids. My plan is to put each of the assorted types of rotations on this page. And, I plan to clean up the expressions so that they are invoked in a proper style for R Studio and Hugo.

````{=html}
```{r, eval=FALSE, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
library(httr)
library(rvest)
library(xml2)

#r3 <- read_html("https://testcite.com/showcase3/?target=test-linearQ15-9c")
#r3 <- read_html("https://testcite.com/showcase3/?target=test-linearQ15-9c,linearQ15-9d,linearQ15-12b")
r3 <- read_html("https://testcite.com/showcase3/?style=rwu&target=complexQ1,imagineQ1,imagineQ2")

ctns_body           <- r3 %>% html_nodes(" body div.ctns-body")
ctns_quiz_container <- r3 %>% html_nodes(" body div.ctns-quiz-container")
ctns_button_group   <- r3 %>% html_nodes(" body div.ctns-button-group")
ctns_results        <- r3 %>% html_nodes(" body div.ctns-results")
ctns_script         <- r3 %>% html_nodes(" body script")

cat(paste(ctns_body,           collapse='' ))
cat(paste(ctns_quiz_container, collapse='' ))
cat(paste(ctns_script,         collapse='' ))
cat(paste(ctns_button_group,   collapse='' ))
cat(paste(ctns_results,        collapse='' ))
```
````

````{=html}
```{r, eval=TRUE, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
library(httr)
library(rvest)
library(xml2)

# See https://f.briatte.org/r/scraping-form-results-with-httr
h <- POST("https://testcite.com/showcase4/?target=rational-functionQ1-1",
    body = list(
        target    = toString(
          c(
            "trinomialD1-1",
            "trinomialD1-1a",
            "binomialD1-1",
            "binomialD1-1a",
            "binomialD1-2",
            "binomialD1-2a",
            "trinomialD1-1",
            "trinomialD1-1a",
            "trinomialD1-2",
            "trinomialD1-2a",
            "polyD1-1",
            "polyD1-1a",
            "polyD1-2",
            "polyD1-2a",
            "polyD2-alt-1",
            "monomialD1-1",
            "monomialD1-1a"
          )),
        style     = "dynamic",
        css       = "border:none;padding:0;",
        quiz_css  = "width:100%;", 
        slide_css = "width:100%;max-width:100%;", 
        reference = "no_reference", 
        divide    = "no_divide"
        )) %>% 
    content("text", encoding = "UTF-8") %>% 
    read_html(encoding = "UTF-8") 
    
ctns_body           <- h %>% html_nodes(" body div.ctns-body")
ctns_quiz_container <- h %>% html_nodes(" body div.ctns-quiz-container")
ctns_button_group   <- h %>% html_nodes(" body div.ctns-button-group")
ctns_results        <- h %>% html_nodes(" body div.ctns-results")
ctns_script         <- h %>% html_nodes(" body script")

cat(paste(ctns_body,           collapse='' ))
cat(paste(ctns_quiz_container, collapse='' ))
cat(paste(ctns_button_group,   collapse='' ))
cat(paste(ctns_results,        collapse='' ))
cat(paste(ctns_script,         collapse='' ))
```
````
