---
title: 1.3. Absolute Value
author: ''
date: '2021-05-08'
slug: 1-3-absolute-value
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2021-05-08T07:46:46-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
math: true
type: book
graphic: true
jplayer: true
src_version: '138'
---

```{r setup, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
require(reticulate)
```

```{python, eval=TRUE, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
sys.path.append('../../../assets/python')

from ctns_make  import ctns_make  as CTNS_MAKE
from ctns_build import ctns_build as CTNS_BUILD
import ctns_form as CTNS

VERSION=138
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
m_list = [
     ['abs_value_1']
#     ['abs_value_prop_4']
#   , ['abs_value_prop_5']
#    ['abs_value_1']
#  , ['abs_value_dist_3']
#  , ['abs_value_prop_1']
#  , ['abs_value_prop_2']
#  , ['abs_value_prop_3']
#  , ['abs_value_prop_4']
#  , ['abs_value_prop_5']
#  , ['abs_value_prop_1_line']
#  , ['abs_value_prop_1_example']
]

for m in m_list:
    CTNS_MAKE(target=m)
    CTNS_BUILD(target=m, id=m[0], version=VERSION, image_target=m[0], opt_ctns = CTNS.FORM_SLIDE_1)
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
m_list = [ 
    ['abs_value_prop_1_lineB']
#    ['axis_x_axis']
#  , ['func_absolute_value']
#  , ['abs_value_dist_1']
#  , ['abs_value_dist_2']
]

for m in m_list:
    CTNS_MAKE(target=m)
    CTNS_BUILD(target=m, id=m[0], version=VERSION, image_target=m[0], opt_ctns = CTNS.FORM_SLIDE_2)
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
m_list = [
     ['abs_value_1_qa']
#    ['abs_value_1_jeopardy']
#  ,  ['abs_value_1b_qa']
#  ,  ['abs_value_2_qa']
#  ,  ['abs_value_2b_qa']
#  ,  ['abs_value_2c_qa']
#  ,  ['abs_value_3_qa']
]

for m in m_list:
    CTNS_MAKE(target=m)
    CTNS_BUILD(target=m, id=m[0], version=VERSION, image_target=m[0], opt_ctns = CTNS.FORM_SLIDE_3, encrypt=False)
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
m_list = [
     ['abs_value_1_qa, abs_value_1b_qa, abs_value_2_qa, abs_value_2b_qa, abs_value_2c_qa, abs_value_3_qa']
]

for m in m_list:
    #CTNS_MAKE(target=m)
    CTNS_BUILD(target=m, id="my_quiz", version=VERSION, opt_ctns = CTNS.FORM_SLIDE_4, encrypt=False)
```

```{python, eval=TRUE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
m_list = [
     ['abs_value_prop_1_example']
]

for m in m_list:
    CTNS_MAKE(target=m)
    CTNS_BUILD(target=m, id=m[0], version=VERSION, image_target=m[0], opt_ctns = CTNS.FORM_SLIDE_5, encrypt=False)
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
m_list = [
#    ['func_absolute_valueS'],
    ['axMscOppoOfXS1']
]

for m in m_list:
    CTNS_MAKE(target=m)
    CTNS_BUILD(target=m, id=m[0], version=VERSION, image_target=m[0], opt_ctns = CTNS.FORM_FLASHCARD_1, encrypt=False)
```

```{python, eval=FALSE, results="asis", echo=FALSE, warning=FALSE, message=FALSE}
m_list = [
    ['abs_value_prop_1S']
]

for m in m_list:
    CTNS_MAKE(target=m)
    CTNS_BUILD(target=m, id=m[0], version=VERSION, image_target=m[0], opt_ctns = CTNS.FORM_FLASHCARD_2)
```

```{r eval=FALSE, echo=FALSE}
blogdown::shortcode('abs_value_1_jeopardy')
```

```{r eval=FALSE, echo=FALSE}
blogdown::shortcode('abs_value_1_qa')
blogdown::shortcode('abs_value_1b_qa')
blogdown::shortcode('abs_value_2_qa')
blogdown::shortcode('abs_value_2b_qa')
blogdown::shortcode('abs_value_2c_qa')
blogdown::shortcode('abs_value_3_qa')
```

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('my_quiz')
```

```{r, echo=FALSE}
blogdown::shortcode_open("spoiler", class="spoiler-left spoiler-bullet", text="<strong>Road Map: Absolute Value</strong>", type="html")
```

- While Algebra 1 introduces the concept of the Absolute Value for the first time, Algebra 2, Pre-Calculus, and even Calculus make liberal use of the concept.

- You want to be nimble with problems involving Absolute Value, not challenged.

- The Absolute Value treats all expressions the same: the negative parts become positive while the positive parts stay the same.

- When you work with Absolute Value there are two categories of problems: EQUALITY and INEQUALITY. With EQUALITY, you are looking for specific numbers. With INEQUALITY, you are looking for a range of values.

- These examples are simple numbers.
\begin{gathered}
| 3 | = 3 \ \ \textrm{ positive numbers } \\ \\
|-5 | = 5 \ \ \textrm{ negative numbers } \\
\end{gathered}

- These examples use a linear expression inside the absolute value.
\begin{gathered}
|  x   | = 6 \ \ \textrm{ what values of } x \textrm{ work here? } \\ \\
| 3x-2 | = 8 \ \ \textrm{ what values of } x \textrm{ work here? } \\
\end{gathered}

- These examples involve inequalities, in which case we are looking for a RANGE of values for x. 
\begin{gathered}
|  x   | < 6 \ \  \textrm{ what range of values for } x \textrm{ work here? } \\ \\
| 3x-2 | <= 8 \ \ \textrm{ what range of values for } x \textrm{ work here? } \\
\end{gathered}

- A simple number line works great with problems involving inequalities, $\lt$, $\le$, $\gt$, and $\ge$.
 
- Remember that when your problem involves $\le$ and $\ge$ the endpoints on your graph are going to be SOLID dots. If your problem involves $\lt$ and $\gt$, then the endpoints on your graph are going to be HOLLOW dots.

- These examples illustrates absolute value expressions on both sides of an inequality. 
\begin{gathered}
|  x   | \lt  | 2x-6   | \ \  \textrm{ what range of values for } x \textrm{ work here? } \\ \\
| 3x-2 | \le | 2x^2 +1| \ \ \textrm{ what range of values for } x \textrm{ work here? } \\
\end{gathered}

- When absolute value expressions on both sides of an inequality, remember that an absolute value can be re-written as two expressions without the absolute value. 
- I definitely graph these problems so that I understand how the answer looks. These ranges can be tricky.

```{r, echo=FALSE}
blogdown::shortcode_close("spoiler", .type="html")
```

## Define Absolute Value

The definition of the Absolute Value states

\begin{equation}
|x| =  
\begin{cases}
\ \ \ x, & \text{if } \ x \ge 0 \\
-x, & \text{if } \ x \lt 0
\end{cases}
\end{equation}

for all real numbers $$x \in \mathbb{R}.$$

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('func_absolute_valueS')
```

## A simple example

For example, 

\begin{equation}
|3| = 3.
\end{equation}

The number $3$ is positive, therefore
$|3| = 3$ from the definition of absolute value,

\begin{equation}
|x| = x \ \ \ \text{when } x \ge 0.
\end{equation}

On the other hand,

\begin{equation}
\begin{aligned}
|-5| = \ & -(-5) \\
     = \ & 5.
\end{aligned}
\end{equation}

The number $-5$ is negative, therefore 
$|-5| = 5$ from the definition of absolute value,

\begin{equation}
|x| = -x \ \ \ \text{when } x \lt 0.
\end{equation}

The absolute value of a negative number equals its opposite.

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('axMscOppoOfXS1')
```


```{r, echo=FALSE}
blogdown::shortcode_open("spoiler", class="spoiler-left spoiler-bullet", text="<strong>Strategy: When you see \\(| N |\\) for some number \\(N\\)</strong>", .type="html")
```

- You know you are working with an absolute value when you see the two vertical bars
\begin{equation}
\LARGE{ | \ \ \ |. }
\end{equation}

- The absolute value of a number makes that number positive. 

- The absolute value of a positive number is the number itself.

- The absolute value of a negative number is the opposite (negative) of the number.

```{r, echo=FALSE}
blogdown::shortcode_close("spoiler", .type="html")
```

Try some examples for yourself.

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_1')
```

## Distance to Zero

The Absolute Value of a number can also be thought of as that number's distance to zero
when graphing the number on a number line.

For example, consider

\begin{equation}
|3| = 3.
\end{equation}

When graphed on a number line, the number $3$ is three units from zero.

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_dist_1')
```

Similarly, consider

\begin{equation}
|-5| = 5.
\end{equation}

When graphed on a number line, the number $-5$ is five units from zero.

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_dist_2')
```

Try some distance examples for yourself.

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_dist_3')
```

## Property: $|x| \ = \ c$

When the absolute value of a
variable $x$ equals a constant $c$, 

\begin{equation}
|x| = c,
\end{equation}

then the variable $x$ equals either of two values, positive $c$ and negative $c$,

\begin{equation}
x = \ \pm \ c.
\end{equation}

```{r, echo=FALSE}
blogdown::shortcode_open("spoiler", text="<strong>Proof: \\(|x| = c \\ \\ \\equiv \\ \\ x = \\pm c\\)</strong>", .type="html")
```

**Proof:**

From the definition of absolute value, the expression

\begin{equation}
|x| = c
\end{equation}

can be re-written as two expressions,

\begin{align}
  |x| = x & = c & \textrm{ when } x \ge 0,
(\#eq:upper-range-equality)
\end{align}

and, 

\begin{align}
  |x| = - x & = - c & \textrm{ when } x \lt 0.
(\#eq:lower-range-equality)
\end{align}

Combining Eqns. \@ref(eq:upper-range-equality) and \@ref(eq:lower-range-equality) gives us our two values
for $x,$

\begin{equation}
x = \pm c.
\end{equation}

```{r, echo=FALSE}
blogdown::shortcode_close("spoiler", .type="html")
```

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_prop_1S')
```


Try these examples for yourself.

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_prop_1')
```

When graphing $|x| = c$ on the number line, label one point for positive $c$ and another for negative $c.$

Try for yourself.

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_prop_1_line')
```

## Using the Property $|x| = c \ \ \ \equiv \ \ \ x = \pm c$

Consider the expression

\begin{equation}
|x - 3| = 5.
(\#eq:example-2)
\end{equation}

Applying the property

\begin{equation}
|x| = c \ \ \  \equiv \ \ \ x = \pm c
\end{equation}

to Eq. \@ref(eq:example-2) expression gives you a new expression,

\begin{equation}
x - 3 = \pm 5.
(\#eq:example-2-new)
\end{equation}

Re-write Eq. \@ref(eq:example-2-new) into two separate expressions, 

\begin{align}
x - 3 & = \ + 5, \textrm{ and } \\\\
x - 3 & = \ - 5.
\end{align}

Solve for $x$ in each case:

\begin{align}
    x - 3 & = \ 5 \\
x - 3 + 3 & = \ 5 + 3\\
    x & = \ 8,
\end{align}

and

\begin{align}
    x - 3 & = \ - 5 \\
x - 3 + 3 & = \ - 5 + 3 \\
        x & = \ - 2.
\end{align}

Graphing these two values of $x$ on the number line gives you

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_prop_1_lineB')
```

Try these examples for yourself.

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_prop_1_example')
```

Consider a second example

\begin{equation}
| 2x - 3 | = 5.
\end{equation}

Just as before, you approach this style of problem using the property

\begin{equation}
|x| = c \ \ \  \equiv \ \ \ x = \pm c.
\end{equation}

First, rewrite the equation into your new equation

\begin{equation}
2x - 3 = \pm 5,
\end{equation}

which translates into two separate equations

\begin{align}
2x - 3 = & \ + 5, \textrm{ and } \\\\
2x - 3 = & \ - 5.
\end{align}

Now, solve for $x$ in each case:

\begin{align}
    2x - 3 = & \ 5 \\
2x - 3 + 3 = & \ 5 + 3\\
        2x = & \ 8\\
  1/2 \cdot (2x) = & \ 1/2 \cdot (8)\\
         x = & \ 4,
\end{align}

and

\begin{align}
    2x - 3 = & \ - 5 \\
2x - 3 + 3 = & \ - 5 + 3\\
        2x = & \ -2 \\
  1/2 \cdot (2x) = & \ 1/2 \cdot (-2) \\
         x= & \ -1.
\end{align}

Our final solution set is the set

\begin{equation}
x = \{ -1, 4 \}.
\end{equation}

## Property: $|x| \lt c$

When the absolute value of a
variable $x$ is less than a constant $c$,

\begin{equation}
|x| \lt c,
\end{equation}

then you can re-write this expression as a range of values for $x,$

\begin{equation}
-c \lt x \lt c.
\end{equation}

Here, values for
$x$ fall somewhere between negative $c$ and positive $c$.

```{r, echo=FALSE}
blogdown::shortcode_open("spoiler", text="<strong>Proof: \\(|x| \\lt c \\ \\ \\equiv \\ \\ -c \\lt x \\lt c\\)</strong>", .type="html")
```

Proof:

From the definition of absolute value, the expression

\begin{equation}
|x| \lt c
\end{equation}

can be written as two expressions,

\begin{align}
  |x| = x& \ \lt c \textrm{ when } x \ge 0,
(\#eq:upper-range)
\end{align}

and, 

\begin{align}
- |x| = x & \ \lt c \textrm{ when } x \lt 0 \\
  |x| = x & \ \gt - c \textrm{ when } x \lt 0.
(\#eq:lower-range)
\end{align}

Combining Eqns. \@ref(eq:upper-range) and \@ref(eq:lower-range) gives us our range for $x$

\begin{equation}
-c \gt x \gt c.
\end{equation}

```{r, echo=FALSE}
blogdown::shortcode_close("spoiler", .type="html")
```

Consider the following inequality,

\begin{equation}
| x | \lt 6.
\end{equation}

By the property 

\begin{equation}
|x| \lt c \ \ \ \equiv \ \ \ -c \lt x \lt c,
\end{equation}

we expand this inequality to read

\begin{equation}
-6 \lt x \lt 6.
\end{equation}

Try some examples for yourself.

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_prop_2')
```

## Property: $|x| \le c$

When the absolute value of a
variable $x$ is less than or equal to a constant $c$,

\begin{equation}
|x| \le c,
\end{equation}

then you can re-write this expression as a range of values for $x,$

\begin{equation}
-c \le x \le c.
\end{equation}

Here, values for
$x$ fall somewhere between negative $c$ and positive $c$, including the two endpoints negative $c$ and positive $c$.

```{r, echo=FALSE}
blogdown::shortcode_open("spoiler", text="<strong>Proof: \\(|x| \\le c \\ \\ \\equiv \\ \\ -c \\le x \\le c\\)</strong>", .type="html")
```

Proof:

From the definition of absolute value, the expression

\begin{equation}
|x| \le c
\end{equation}

can be written as two expressions,

\begin{align}
  |x| = x& \ \le c \textrm{ when } x \ge 0,
(\#eq:upper-range)
\end{align}

and, 

\begin{align}
- |x| = x & \ \le c \textrm{ when } x \le 0 \\
  |x| = x & \ \ge - c \textrm{ when } x \le 0.
(\#eq:lower-range)
\end{align}

Combining Eqns. \@ref(eq:upper-range) and \@ref(eq:lower-range) gives us our range for $x$

\begin{equation}
-c \ge x \ge c.
\end{equation}

```{r, echo=FALSE}
blogdown::shortcode_close("spoiler", .type="html")
```

Consider the following inequality,

\begin{equation}
| x | \le 6.
\end{equation}

By the property 

\begin{equation}
|x| \le c \ \ \ \equiv \ \ \ -c \le x \le c,
\end{equation}

we expand this inequality to read

\begin{equation}
-6 \le x \le 6.
\end{equation}

Try some examples for yourself.

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_prop_3')
```

## Solving

Write more here.

----

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('func_absolute_valueS')
blogdown::shortcode('func_absolute_valueS')
blogdown::shortcode('func_absolute_valueS')
blogdown::shortcode('func_absolute_valueS')
blogdown::shortcode('func_absolute_valueS')
blogdown::shortcode('func_absolute_valueS')
blogdown::shortcode('func_absolute_valueS')
blogdown::shortcode('func_absolute_valueS')
```

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('axis_x_axis')
#blogdown::shortcode('func_absolute_value')
```

----

```{r eval=TRUE, echo=FALSE}
blogdown::shortcode('abs_value_1')
blogdown::shortcode('abs_value_prop_4')
blogdown::shortcode('abs_value_prop_5')
blogdown::shortcode('abs_value_1')
blogdown::shortcode('abs_value_dist_3')
blogdown::shortcode('abs_value_prop_1')
blogdown::shortcode('abs_value_prop_2')
blogdown::shortcode('abs_value_prop_3')
blogdown::shortcode('abs_value_prop_4')
blogdown::shortcode('abs_value_prop_5')
blogdown::shortcode('abs_value_prop_1_line')
blogdown::shortcode('abs_value_prop_1_example')
```

