---
title: Week 1 - R Program
author: ''
date: '2021-01-26'
slug: week-1-r-program
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2021-01-26T08:10:48-05:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
math: true
---

This programming example illustrates how to create and graph the results from a random experiment in which a population is tested for an infection, where a test may yield a True Positive or a False Positive result.

We begin by setting our experiment parameters: the total population size of $N$ and a known infection rate of $p$. 

```{r, echo=TRUE}
    N = 50   # The population contains of N=1000 members.
    p = .8   # The infection rate for a population member is assumed to be p.
```


Next, we create a vector $B$ to represent a sample population where each element $b_i \in B$ corresponds to the health status of a population member $i$, such that

::: {.highlight .transparent style="font-size:0.7rem;color:#998;margin-left:2em"}
$b_i == 1$ means member $i$ is infected, and <br/>
$b_i == 0$ means member $i$ is not infected (healthy).
:::

Given the population size $N$ and an infection rate $p$, we create vector $B$ from values drawn randomly _with replacement_ from a vector $c(0,1)$, where we assign $1$ with probability $p$, and $0$ with probability $1-p$.

```{r, echo=TRUE}
    # Create a random sample population from a vector c(0,1) where assigning
    # the value '0' denotes a healthy member whereas assigning a '1' denotes
    # an infected member of the population member.
    #
    B = sample(c(0,1), N, prob=c(1-p,p), replace=TRUE)
```

```{r, echo=FALSE, eval=FALSE}
    # Show interim results.
    sprintf(
      fmt="population total: %d, population total with disease: %d, likelihood of disease: %d%%", 
      length(B), 
      sum(B),
      floor(100*p))
```


Next, we assume a pair of likelihood values: 
the probability of a positive test when a population member is infected,
and the probability of a positive test when they are not.

```{r, echo=TRUE}
    # Set likelihood for a positive test whether a member is
    # is infected or not.
    #
    pr_positive_test_when_infected = 0.999
    pr_positive_test_when_healthy  = 0.005
```


For our random experiment, we begin with a vector $u$ of random floating-point values selected in the range $(0,1)$ using a uniform distribution.

```{r, echo=TRUE}
    # Generate N random (floating-point) numbers uniformly
    # in the default range (0,1).
    #
    u = runif(N)
```


Now, we create a vector $A$ that denotes our test results for our population $B$, such that every element $a_i \in A$ corresponds to the test results of a population member $b_i \in B$ where

::: {.highlight .transparent style="font-size:0.7rem;color:#998;margin-left:2em"}
$a_i == 1$ means member $i$ is tested positive, and <br/>
$a_i == 0$ means member $i$ is tested negative.
:::

In our random experiment, we consider the following conditional probabilities,

::: {.highlight .transparent style="font-size:0.7rem;color:#998;margin-left:2em"}
$Pr(A|B == 0) == Pr( \text{positive test} | \text{member is healthy}),$<br/>
$Pr(A|B == 1) == Pr( \text{positive test} | \text{member is infected})$
:::

In one very short expression, we calculate the conditional probabilities above.

```{r, echo=TRUE}

    # Calculate the conditional probabilities
    #
    #    Pr(A|B == 0) = pr_positive_test_when_healthy
    #    Pr(A|B == 1) = pr_positive_test_when_infected, 
    #
    # Note, the following seriously abridged statement is equivalent
    # to the C-Language nested if-else statement,
    #
    # if (b == 1) {
    #
    #   // Assign '1' if <, '0' otherwise.
    #   a = u < pr_positive_test_when_infected;
    #
    # } else {
    #
    #   // Assign '1' if <, '0' otherwise.
    #   a = u < pr_positive_test_when_healthy;
    #
    # }
    #
    A = ifelse(B==1, u<pr_positive_test_when_infected, u<pr_positive_test_when_healthy)
```

Given $A$ and $B$, we can calculate an empirical value for the conditional probability,

\begin{equation}
Pr(B | A) = \frac{Pr(A \cap B)}{Pr(A)},
\end{equation}

which expresses the probability that a population member is _indeed_ sick given their test came back positive. In this case, credit to this conditional probability depends not only on how many members tested positive $n(A)$, but also on whether that member who tested positive was actually sick. 

```{r, echo=TRUE}
    nBA = sum(B & A)    # Count the number of infected members who tested positive
    nA = sum(A)         # Count the number of members who tested positive
    pBgivenA = nBA/nA   # Compute Pr(B|A) as Pr(B&A)/Pr(B)
```

Wrapping this entire process into a single routine that runs as a function of infection rate $p$, and then invoking that function over a range of infection rates yields an interest result. 

As shown in Figure \@ref(fig:ratio), the conditional probability $Pr(B|A)$ is inversely proportional to the infection rate. This is to say that the greater the infection rate, the closer the conditional probability $Pr(B|A)$ comes to equalling the infection rate itself $Pr(B)$. In short, 

::: highlight
As the true infection rate $p$ increases, the conditional probability of the measured infection rate $Pr(B|A)$ approaches the measured infection rate $Pr(B)$ and as such becomes independent of the efficacy of the test.
:::

From another view point, Figure \@ref(fig:constant) shows that the conditional probability $Pr(B|A)$ approaches a constant $Pr(B)$ for increasing values of infection rates $p$.

```{r, echo=FALSE}
    f <- function(p=0.02){
    
      N = 10000   # The population contains of N=10000 members.
      B = sample(c(0,1), N, prob=c(1-p,p), replace=TRUE)

      pr_positive_test_when_infected = 0.999
      pr_positive_test_when_healthy  = 0.005
      
      u = runif(N)
      
      A = ifelse(B==1, u<pr_positive_test_when_infected, u<pr_positive_test_when_healthy)

      nBA = sum(B & A)
      nA = sum(A)
      nB = sum(B)
      pBgivenA = nBA/nA
      
      #return(pBgivenA/(nB/N))
      return(pBgivenA)
    }
```

```{r ratio, echo=FALSE, fig.cap="$Pr(B|A)/p$ is inversely proportional to $p$"}
    cnt = 100
    pgrid <- seq(from=0.001,to=0.5,length=cnt)
    y <- rep(0,cnt)
    for(i in 1:cnt) y[i] <- f(pgrid[i])/pgrid[i]
    plot(pgrid, y, type="l", xlab="p", ylab="Pr (B|A) / p")
    #plot(pgrid, y, type="l", bty="l", xlab="p", ylab="Pr(A|B)/p")
    pr_positive_test_when_infected = 0.999
    abline(h=pr_positive_test_when_infected,lty=2,col=2)
```

```{r constant, echo=FALSE, fig.cap="$Pr(B|A)$ approaches a constant $Pr(B)$ for increasing values of $p$."}
    cnt = 100
    pgrid <- seq(from=0.001,to=0.5,length=cnt)
    y <- rep(0,cnt)
    for(i in 1:cnt) y[i] <- f(pgrid[i])
    plot(pgrid, y, type="l", xlab="p", ylab="Pr (B|A) / p")
    #plot(pgrid, y, type="l", bty="l", xlab="p", ylab="Pr(A|B)/p")
    pr_positive_test_when_infected = 0.999
    abline(h=pr_positive_test_when_infected,lty=2,col=2)
```
